Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-20 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
dora section updated

We base our work on Dora, a mobile cognitive robot with a pre-existing multi-layered spatial model~\cite{Hawes/etal:2011}. In this paper, we draw on the metric layer of this model. For more information on Dora's other competences, see recent papers, e.g.~\cite{Hawes/etal:2011,Hanheide/etal:2011}.

Dora's metric layer is a collection of lines in a 2D global coordinate frame. These lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

% Objects
Dora is capable of using vision to recognize predefined objects. Recognition can either be triggered through autonomous visual search or a a user's command. When an object is detected it is represented in the place layer relative to Dora's current position. The recognizer associates each object with a label that was provided during a training phase. In our current work, these labels are used directly in analogical processing. We use a convex hull around the places in a room to represent its area, and the 2D locations of perceived objects to create the qualitative spatial representations in the next section.

lines = walls

% simulation
As the purpose of this paper is to explore the possibility of using qualitative spatial reasoning and analogy on top of Dora's spatial model, we decided to perform our research using the Player/Stage hardware abstraction layer and simulation tools~\cite{GerkeyVaughanHoward03} rather than on a real robot. This allows us to run the Dora system \emph{mostly unchanged} in a controlled simulation environment, rather than deal with some of the unrelated challenges of running the robot in the real world. The key difference is that the sensor readings are free of noise in the simulated world. This is particularly significant where vision is concerned, as Dora's object recognizer is replaced entirely by a simulated blob detector which is always correct. Beyond this, the functionality of the system remains unchanged, and, crucially, the representations our work builds on will be the same when the system is run in the real world.

>>>>

We base our work on Dora, a mobile cognitive robot with a pre-existing multi-layered spatial model~\cite{Hawes/etal:2011}. In this paper, we draw on the metric map from this model. For more information on Dora's other competences, see recent papers, e.g.~\cite{Hawes/etal:2011,Hanheide/etal:2011}.

Dora's metric map is a collection of lines in a 2D global coordinate frame. These lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

Dora is capable of using vision to recognize pre-trained 3D object models. Recognition can either be triggered through autonomous visual search or at a user's command. When an object is detected it is represented in the metric map 
by placing a copy of the model at the detected pose. The recognizer associates each object with a type label that was provided during a training phase.

To enable us to generate a range of different evaluation situations in a reasonable length of time, we have generated data from Dora in both real rooms and in simulation. Simulation is performed using the Player/Stage hardware abstraction layer~\cite{GerkeyVaughanHoward03} allowing us to run the system \emph{mostly unchanged} in a pre-defined environment. Also, to enable us to detect a wider range of objects than is usually possible (from armchairs to whiteboards), we used a simulated object recogniser in all runs. The recogniser was configured with types and positions of objects in the environment and was guaranteed to detected them when the robot was orientated towards them. This eliminated any errors from the recognition process, but was still influenced by errors in robot localisation.
